Comments on Latent Ranking

### 2021-06-07 output_scripts/Paper_Plots.Rmd
update overall predict to also save the median mae for all cohorts for second plot (fig7a in paper)
also tidying up and renaming some old stan files which aren't used to avoid any possible confusion

<!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->

@@

## Figure 8a: Frobenius norm of interaction predictions, single cohort

@@

```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
load("../output/plot_N_predict.RData")
# current_cohort <- 5# cohort 1 looks worse than rest
# 3 looks nice

temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)
p3_slides <- temp_plot_df %>%
  filter(method != "I-MMHP") %>%
  rowwise() %>%
  #mutate(norm = min(norm,100)) %>%
  ggplot( aes(x = method, y = mae, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 10) +
  NULL
p3_slides
```

@@

```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4.5, eval=FALSE}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm))

@@

save(sim_dsnl_active, fit_dsnl_active, utility_state_day,
     sim_dsnl_inactive, fit_dsnl_inactive, social_state_day,
     file = paste(data_path,cohort_names[current_cohort],
                  "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
                  ".RData",sep=''))
rm(interpolation_array_list)
rm(state_array_list)
rm(termination_state_list)
rm(initial_state_list)
```

@@

```{r fig-10b-rank-correlation}
par(mar=c(3,5,3,1))
cx <- 1.75  # cex for axis label text; 
# default is 1. bigger numbers make the text bigger, smaller, smaller.  
x.ttl <- ""; # blank x-axis label  
y.ttl <- "rank corr. (Glicko rank)";  
ttl <- "(b)";  
#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
# y-axis limits. +2 at top to give room for legend  
y.lim <- c(-1,1.2)    
x.lim <- c(0.5, (length(task.types))) 
cols <- c('paleturquoise4', 'lightgreen', 'cornsilk')
shifts <- c(-0.25, 0, 0.25)

>>>>

@@

## Figure 8a: MAE of interaction predictions, single cohort

@@

@@

```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4.5, eval=FALSE}
### updated to mae

load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_mae_df %>% 
  group_by(day, method) %>% 
  summarise(avg = mean(norm), n = n(), sd = sd(norm))

@@

save(sim_dsnl_active, fit_dsnl_active, utility_state_day,
     sim_dsnl_inactive, fit_dsnl_inactive, social_state_day,
     file = paste(data_path,cohort_names[current_cohort],
                  "/dsnl_state_separation_stan_result_",
                  cohort_names[current_cohort],
                  ".RData",sep=''))
rm(interpolation_array_list)
rm(state_array_list)
rm(termination_state_list)
rm(initial_state_list)
```

@@

```{r fig-10b-rank-correlation}
par(mar=c(3, 5, 3, 1))
cx <- 1.75  # cex for axis label text; 
# default is 1. bigger numbers make the text bigger, smaller, smaller.  
x.ttl <- ""; # blank x-axis label  
y.ttl <- "rank corr. (Glicko rank)";  
ttl <- "(b)";  
#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
# y-axis limits. +2 at top to give room for legend  
y.lim <- c(-1,1.2)    
x.lim <- c(0.5, (length(task.types))) 
cols <- c('paleturquoise4', 'lightgreen', 'cornsilk')
shifts <- c(-0.25, 0, 0.25)

### 2021-06-07 output_scripts/revisions_may.Rmd
update overall predict to also save the median mae for all cohorts for second plot (fig7a in paper)
also tidying up and renaming some old stan files which aren't used to avoid any possible confusion

@@

```{r fig4b-redone}
y.ub <- c(35,35,35)#c(130,72,31)
x_events <- 190#135#150
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#160#200#130
my.long.x <- 205#205#134.5
legend.x <- c(60,60,60)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(23,23,23)#c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue')
positive.col <- add.alpha('tomato')
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

model_colors <- col_df %>% filter(method %in% c("C-HP",
                                                "C-DCHP",
                                                "C-MMHP"))

@@

drawUniMMHPIntensityPaper(true.object,
                          simulation = fixStateTransition(test.mmhp),
                          yupper=y.ub[1], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2,
                          min.x=0, max.x=my.xlim,
                          title_name=paste(plot.i,"->",plot.j),
                          title.cex = 2,
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,
                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                                   model1_par_est$f[plot.j],
                                                   model1_par_est$eta_1,
                                                   model1_par_est$eta_2,
                                                   model1_par_est$eta_3),
                         beta=model1_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[1],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])

## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)

## add legend
# changed 34 to 23, 25 to 18, -20 to -10
# legend(10,legend.y[1],c("State 1/0 events","State change point"),
#        col = c(NA,"red"),
#        y.intersp=0.85,x.intersp=-0.1, bty = "n",
#        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
#        lty = c(NA,NA), lwd=c(NA,4))
# points(29,84,pch=1,cex=2,col="blue")
# points(26,84,pch=16,cex=2,col="blue")
legend(legend.x[1],legend.y[1],c("True"),
       col = c("black"),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
legend(legend.x[1]+22,legend.y[1],c("C-HP"),
       col = c(model_colors[1]),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now ###
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.positive,0),col=positive.col,border=NA)

axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

# model2
############
drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[2], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
                           model2_par_est$zeta[plot.j],
                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
                                                   model2_par_est$f[plot.j],
                                                   model2_par_est$eta_1,
                                                   model2_par_est$eta_2,
                                                   model2_par_est$eta_3),
                         beta=model2_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[2],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])
legend(legend.x[2],legend.y[2],"C-DCHP",
       col = model_colors[2],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)

axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)

legend(legend.x[2]-50,
       legend.y[2]+2,c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.5, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,2))
points(legend.x[2]-46,legend.y[2] - 4.5, pch = 1, cex = 2, col = "blue")
points(legend.x[2]-44,legend.y[2] - 4.5, pch = 16, cex = 2, col = "blue")

## delta lambda
par(mar = c(0,0.3,0,0.1))
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t

plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
     ylim=c(-4,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

# model3
########
par(mar = c(0,0.3,1,0.1))
drawUniMMHPIntensityPaper(true.object,
                          simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[3],
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawUniMMHPIntensityPaper(object_hat,
                          simulation = list(
                            x=state.est.latent.mmhp.new$x.hat,                                          
                            z=state.est.latent.mmhp.new$z.hat,
                            tau=test.mmhp$tau,zt=test.mmhp$zt,
                            lambda.max=test.mmhp$lambda.max),
                          yupper=y.ub,add=TRUE,
                          color=add.alpha(model_colors[3],
                                          alpha=line.alpha[2]),
                          line.width=line.wdth[2])
legend(legend.x[3],legend.y[3],"C-MMHP",
       col = model_colors[3],
       y.intersp=0.6,x.intersp=0.1,bty = "n",
       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)

legend(legend.x[3]-50,legend.y[3]+2, c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.75,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m3-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

## top
mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)

### just need to adjust the scales really!

>>>>

```{r get-days-above-plot}
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(
  current_cohort, 
  raw_df =  full_data[[cohort_names[current_cohort]]],
  clean_data)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_days <- unique(return_df[, 
                                       c("observe.id", "observe.time", "day")])

unique_observe_days %>% 
  filter(observe.id %in% start_win)

unique_observe_days %>% 
  filter(observe.id %in% end_win)

@@

```{r fig4b-redone}
y.ub <- c(4, 5, 3) # c(130,72,31)
x_events <- 190 # 135#150
layout(matrix(c(1:6), 6, 1), heights = rep(c(7.5, 2.5), 3))
my.xlim <- 200 # 160#200#130
my.long.x <- 205 # 205#134.5
legend.x <- c(60, 60, 60) # c(135,135,135)
legend.y <- # c(34,32,32)
legend.y <- c(2, 2, 2) # c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 # 3
line.alpha <- c(0.9, 0.6)
line.wdth <- c(2, 2.5)
negative.col <- add.alpha("lightskyblue")
positive.col <- add.alpha("tomato")

par(
  mar = c(0, 0.3, 0, 0.1), oma = c(0, 3.5, 4, 0),
  tcl = 0.2, mgp = c(0.5, 0, 0), xpd = TRUE
)

model_colors <- col_df %>% filter(method %in% c(
  "C-HP",
  "C-DCHP",
  "C-MMHP"
))

@@

drawUniMMHPIntensityPaper(true.object,
  simulation = fixStateTransition(test.mmhp),
  yupper = y.ub[1],
  color = add.alpha("black", alpha = line.alpha[1]),
  line.width = line.wdth[1],
  y.ratio = -0.05, min.y = -0.5,
  min.x = 0, max.x = my.xlim,
  title_name = paste(plot.i, "->", plot.j),
  title.cex = 2,
  box.type = "n"
)
drawHawkesIntensityPaper(
  lambda0 = model1_par_est$lambda0,
  alpha = model1_fn$alpha.fun(
    model1_par_est$f[plot.i],
    model1_par_est$f[plot.j],
    model1_par_est$eta_1,
    model1_par_est$eta_2,
    model1_par_est$eta_3
  ),
  beta = model1_par_est$beta,
  events = test.mmhp$tau,
  color = add.alpha(model_colors[1],
    alpha = line.alpha[2]
  ),
  line.width = line.wdth[2]
)

# draw box
axis(1,
  at = c(-2, my.long.x),
  col = "gray35",
  line = 0.5,
  tick = T,
  labels = rep("", 2),
  lwd = 0.5,
  lwd.ticks = 0,
  lty = 3
)

## add legend
# changed 34 to 23, 25 to 18, -20 to -10
# legend(10,legend.y[1],c("State 1/0 events","State change point"),
#        col = c(NA,"red"),
#        y.intersp=0.85,x.intersp=-0.1, bty = "n",
#        pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
#        lty = c(NA,NA), lwd=c(NA,4))
# points(29,84,pch=1,cex=2,col="blue")
# points(26,84,pch=16,cex=2,col="blue")

#### more legend
# legend(legend.x[1], legend.y[1], c("True"),
#   col = c("black"),
#   y.intersp = 0.88, x.intersp = 0.15, bty = "n",
#   lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
# )
# legend(legend.x[1] + 22, legend.y[1], c("C-HP"),
#   col = c(model_colors[1]),
#   y.intersp = 0.88, x.intersp = 0.15, bty = "n",
#   lty = c(1), lwd = c(5), cex = legend.cex, seg.len = 1
# )

## delta lambda
par(mar = c(0, 0.3, 0, 0.1))
plot(0, 0,
  xlim = c(0, my.xlim), 
  ylim = c(-1, 1),
  type = "n",
  bty = "n",
  xlab = "",
  ylab = "",
  xaxt = "n",
  yaxt = "n",
  axes = FALSE
)
delta.lambda <- lambda.m1$lambda.t - lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive < 0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative > 0] <- 0
### hiding these for now ###
polygon(c(0, lambda.true$time.vec, x_events), # 200
  c(0, delta.negative, 0),
  col = negative.col, border = NA
)
polygon(c(0, lambda.true$time.vec, x_events), # 200
  c(0, delta.positive, 0),
  col = positive.col, border = NA
)

axis(1,
  at = c(-1, my.long.x), 
  col = "gray35",
  line = 0, tick = T, 
  labels = rep("", 2),
  lwd = 0.7,
  lwd.ticks = 0
)

# model2
############
drawUniMMHPIntensityPaper(true.object,
  simulation = fixStateTransition(test.mmhp),
  yupper = y.ub[2],
  color = add.alpha("black", alpha = line.alpha[1]),
  line.width = line.wdth[1],
  y.ratio = -0.05,
  min.y = -0.5,
  min.x = 0,
  max.x = my.xlim,
  box.type = "n"
)
drawHawkesIntensityPaper(
  lambda0 = model2_par_est$gamma[plot.i] +
    model2_par_est$zeta[plot.j],
  alpha = model1_fn$alpha.fun(
    model2_par_est$f[plot.i],
    model2_par_est$f[plot.j],
    model2_par_est$eta_1,
    model2_par_est$eta_2,
    model2_par_est$eta_3
  ),
  beta = model2_par_est$beta,
  events = test.mmhp$tau,
  color = add.alpha(model_colors[2],
    alpha = line.alpha[2]
  ),
  line.width = line.wdth[2]
)

### used legend
# legend(legend.x[2], legend.y[2], "C-DCHP",
#   col = model_colors[2],
#   y.intersp = 0.88,
#   x.intersp = 0.1,
#   bty = "n",
#   lty = 1,
#   lwd = 5,
#   cex = legend.cex,
#   seg.len = 1
# )

axis(1,
  at = c(-2, my.long.x),
  col = "gray35",
  line = 0.5,
  tick = T,
  labels = rep("", 2),
  lwd = 0.5,
  lwd.ticks = 0,
  lty = 3
)

## location of legend
# legend(legend.x[2] - 50,
#   legend.y[2] + 1, c("State 0/1 events", "State change point"),
#   col = c(NA, "red"),
#   y.intersp = 0.85, x.intersp = -0.5, bty = "n",
#   pch = c(NA, 4), pt.cex = c(NA, 2), cex = legend.cex,
#   lty = c(NA, NA), lwd = c(NA, 2)
# )
# points(legend.x[2] - 46, legend.y[2] - .5, pch = 1, cex = 2, col = "blue")
# points(legend.x[2] - 44, legend.y[2] - .5, pch = 16, cex = 2, col = "blue")

## delta lambda
par(mar = c(0, 0.3, 0, 0.1))
delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t

plot(lambda.true$time.vec, delta.lambda,
  xlim = c(0, my.xlim),
  ylim = c(-1, 1.5), type = "n",
  bty = "n",
  xlab = "",
  ylab = "",
  xaxt = "n",
  yaxt = "n",
  axes = FALSE
)
delta.lambda <- lambda.m2$lambda.t - lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive < 0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative > 0] <- 0
polygon(c(0, lambda.true$time.vec, x_events), # 200
  c(0, delta.negative, 0),
  col = negative.col, border = NA
)
polygon(c(0, lambda.true$time.vec, x_events), # 200
  c(0, delta.positive, 0),
  col = positive.col, border = NA
)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,
  at = c(-2, my.long.x), col = "gray35",
  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
)

# model3
########
par(mar = c(0, 0.3, 1, 0.1))
drawUniMMHPIntensityPaper(true.object,
  simulation = fixStateTransition(test.mmhp),
  yupper = y.ub[3],
  color = add.alpha("black", alpha = line.alpha[1]),
  line.width = line.wdth[1],
  y.ratio = -0.05, min.y = -0.5, min.x = 0, max.x = my.xlim,
  box.type = "n"
)
drawUniMMHPIntensityPaper(object_hat,
  simulation = list(
    x = state.est.latent.mmhp.new$x.hat,
    z = state.est.latent.mmhp.new$z.hat,
    tau = test.mmhp$tau, zt = test.mmhp$zt,
    lambda.max = test.mmhp$lambda.max
  ),
  yupper = y.ub, add = TRUE,
  color = add.alpha(model_colors[3],
    alpha = line.alpha[2]
  ),
  line.width = line.wdth[2]
)
# legend(legend.x[3], legend.y[3], "C-MMHP",
#   col = model_colors[3],
#   y.intersp = 0.6,
#   x.intersp = 0.1,
#   bty = "n",
#   lty = 1,
#   lwd = 5,
#   cex = legend.cex,
#   seg.len = 1
# )
## draw box
axis(1,
  at = c(-2, my.long.x),
  col = "gray35",
  line = 0.5,
  tick = T,
  labels = rep("", 2), 
  lwd = 0.5,
  lwd.ticks = 0, lty = 3
)

# legend(legend.x[3] - 50, legend.y[3] + 2,
#        c("Overestimation", "Underestimation"),
#   col = c(positive.col, negative.col),
#   y.intersp = 0.75, x.intersp = 0.5, bty = "n",
#   lty = c(1, 1), lwd = c(10, 10), cex = legend.cex, seg.len = 0.8
# )

## delta lambda
par(mar = c(0, 0.3, 0, 0.1))
plot(0, 0,
  xlim = c(0, my.xlim), ylim = c(-1, 1.5), type = "n",
  bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
)
delta.lambda <- lambda.m3 - lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive < 0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative > 0] <- 0
### hiding these for now
polygon(c(0, lambda.true$time.vec, x_events), # 200
  c(0, delta.negative, 0),
  col = negative.col, border = NA
)
polygon(c(0, lambda.true$time.vec, x_events), # 200
  c(0, delta.positive, 0),
  col = positive.col, border = NA
)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,
  at = c(-2, my.long.x), col = "gray35",
  line = 0, tick = T, labels = rep("", 2), lwd = 0.7, lwd.ticks = 0
)

# ## top
# mtext(text = "(b)", side = 3, line = 0.8, outer = TRUE, cex = 2.5, font = 2)
# ## bottom
# mtext(text = "Time", side = 1, line = 2, outer = TRUE, cex = 2.25)
# ## left
# mtext(text = "Intensity", side = 2, line = 0.6, outer = TRUE, cex = 2.25)
